resistanceModelNotesAndy

### 2015-04-27 resistanceModelNotesAndy.Rmd
progress notes

@@

1. continue with getting classificatrion trees working in sensiAn1

>>>>

**22/4/15** jury service 11.30 - 12.30 1 hr

```{r}
out <- sensiAn1( nScenarios = 10, h.RS1_A0=c(0.1,1))
```

**24/4/15** 4-5 1hr

**27/4/15** 9.15-13.15 4hrs

trying to test rpart in sensiAn1
getting :
cfit <- rpart(res ~ h.RS1_A0 + h.RS2_0B, data = forCT, method = 'class')
Error in cbind(yval2, yprob, nodeprob) : 
  number of rows of matrices must match (see arg 2)

This was because there were some NAs in the results that can from where a resistance frequency of 0.5 was not reached.
so I temp converted them to 999

Now get :
Error in plot.rpart(cfit) : fit is not a tree, just a root

Is this because I haven't used enough samples or because it doesn't work with just 2 predictors ?

Trying with more samples, still get same error :

`inputAndResults <- sensiAn1( 100, h.RS1_A0=c(0.1,1), h.RS2_0B=c(0.1,1) )`

more samples and more inputs I do get a tree
`inputAndResults <- sensiAn1(500, h.RS1_A0=c(0.1,1), h.RS2_0B=c(0.1,1), s.RR1_A0=c(0.2,1), s.RR2_0B=c(0.2,1))`

Some of susanas code for finessing the tree :
tree->rpart(outcome ~ h_n+ h_o+h_I+s_o+s_I+φ_o+φ_I+α_o+α_I+α_fn+α_mo+α_mI+α_mn+z+beta_f+β_m ,method='class',data=working_example,control=rpart.control(minsplit=50))

# control=rpart.control(minsplit=50)
# minsplit	the minimum number of observations that must exist in a node in order for a split to be attempted.
# then prune the tree to avoid overfitting the data
pruned_tree<- prune(tree, cp=tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"])

@@

1. continue with getting classification trees working in sensiAn1
